Spin canonical rings of log stacky curves

### 2016-01-18 curves-write-up/spin-cring.tex
fixed todos

\sssec*{Idea of proof:}\todo{Update subsection}
The proof will be fairly involved. To show part (a), we 
first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
We then use Riemann--Roch
to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
show that the set of elements we produce forms a basis.

@@

Cohn's geometric interpretation of Hirzebruch--Jung fractions, as described in 
\cite{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities} 
yields an explicit formula for these primitives, as given in \cite[Proposition 4.3]{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities}.
All primitives lie in degrees at most $\beta$
(since points in degree $\gamma=\beta+\omega$ can be written as a sum of points
in degree $\beta$ with those in degree $\omega$).  Note that if two primitives
had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$
and thus could not both be generators. So, all the $c_i$'s (the $y$-coordinates
of the primitives) are distinct, and we may assume $c_i<c_{i+1}$ for
all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be
at most one new primitive,
\todo{Aaron: What does ``new'' primitive mean? Does it mean the same thing as ``at most one primitive''
without the word new?}
since we can construct points with $y$ coordinates
between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in
degree 1 and degree $k-1$, and these new primitives have pole order greater
than all primitives of smaller $x$-coordinate.  Therefore, the ordering of
primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values
$k_i$ are in weakly increasing order.  Finally, let $y_1, \ldots, y_n$
be elements of $R_Lx$
\todo{Aaron: What is $R_Lx$? Should this just be $R_L$?}
with pole orders given by $c_1,\ldots, c_n$ and degrees
given by the $x$ coordinates of the corresponding primitives.
%We will the use positive best lower approximations to
%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
%
%Let 
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
%	\beta}
%\]
%
%\noindent
%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
%\[
%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
%\]
%so the mediant inequality tells us
%\[
%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
%\]
%Multiplying through by $k_i$ gives
%\[
%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
%\]

@@

\noindent
Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S\cup S_0$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$. \todo{Check whether all these $S$ need to be changed to $S\cup S_0$ like here.}   
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S\cup S_0$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S\cup S_0$.

@@

Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for some $l$.  Then, for all $r< h$ we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.  Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.  Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.  
Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ meaning that $\sum_{j=1}^r \gamma_j c_j < c_{r+1}$, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.

>>>>

\sssec*{Idea of proof:}
The proof will be fairly involved. To show part (a), we use Riemann-Roch to reduce the
problem to one of finding primitives of cones; we then apply previous work on continued fractions to deduce these primitives.  We conclude this part of the problem, showing by dimension count, that these primitives induce all the generators of $R_L$ over $R_L$'.

first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
We then use Riemann--Roch
to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
show that the set of elements we produce forms a basis.

@@

Cohn's geometric interpretation of Hirzebruch--Jung fractions, as described in 
\cite{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities} 
yields an explicit formula for these primitives, as given in \cite[Proposition 4.3]{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities}.
All primitives lie in degrees at most $\beta$
(since points in degree $\gamma=\beta+\omega$ can be written as a sum of points
in degree $\beta$ with those in degree $\omega$).  Note that if two primitives
had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$
and thus could not both be generators. So, all the $c_i$'s (the $y$-coordinates
of the primitives) are distinct, and we may assume $c_i<c_{i+1}$ for
all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be
at most one primitive,
since we can construct points with $y$ coordinates
between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in
degree 1 and degree $k-1$, and these new primitives have pole order greater
than all primitives of smaller $x$-coordinate.  Therefore, the ordering of
primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values
$k_i$ are in weakly increasing order.  Finally, let $y_1, \ldots, y_n$
be elements of $R_L$
with pole orders given by $c_1,\ldots, c_n$ and degrees
given by the $x$ coordinates of the corresponding primitives.
%We will the use positive best lower approximations to
%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
%
%Let 
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
%	\beta}
%\]
%
%\noindent
%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
%\[
%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
%\]
%so the mediant inequality tells us
%\[
%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
%\]
%Multiplying through by $k_i$ gives
%\[
%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
%\]

@@

\noindent
Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S\cup S_0$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$.  
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S\cup S_0$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S\cup S_0$.

@@

Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that
$\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for
some $l$.  Then, for all $r< h$ we have $\prod_{j=1}^r
{y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have
$\prod_{j=1}^r {y_j}^{\omega_j}\in S$.  Furthermore, since $(\gamma_1,
\ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous
condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.  Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.  
Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ meaning that $\sum_{j=1}^r \gamma_j c_j < c_{r+1}$, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.
